SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-07 conc.tex
wording

\section{Conclusion}
\label{Conclusion}
In this paper, we introduce perceptron-based learning for prefetching.  The
perceptron filter acts independently as a check on the underlying prefetch
engine.  PPF improves performance over the base prefetcher by 11.9\%.  We
believe that this is a robust and adaptable technique that can be used to
enhance any existing and upcoming prefetchers.

>>>>

\section{Conclusion}
\label{Conclusion}
In this paper, we introduce the Perceptron-Based Prefetch Filtering
(PPF).  PPF acts as an independent check on the quality of predictions
made by the underlying prefetch engine.  We also created a case study
implementation of PPF using SPP as the baseline prefetch engine, while
in principle other prefetchers could be used.  We show that PPF
effectively filters bad prefetches, such that the given underlying
prefetcher can be highly aggressively tuned to achieve increasing
coverage.  PPF improves performance over the base prefetcher by up to
11.4\%.  PPF is a robust and adaptable technique that can be used to
enhance any existing prefetcher and can be a valuable tool in the
design of future memory latency constrained systems.
